---
title: "HomeTask"
author: "Jingying Weng"
date: "2022/6/30"
output:
  pdf_document: 
    latex_engine: xelatex
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

## Main questions:

### Question 1: Given a length 4 vector V, and two numbers N<M, what is the probability to find two components a and b from V that a >= N and b >= M (task 1).

* Randomly select two out of 4 abilities, check if I can fulfill the 2 requirement. randomly select one of the two to be higher and another to be lower. Is it same to select on higher and select one lower from remaining?

Possible combinations:

2-1: Choose(4,2) = `r choose(4,2)` multiply 2 = 12

4-3: Choose(4,1) multiply Choose(3,1) = 12

So we have 12 possible combinations of tasks.

<br>

* Then the probability to fulfill the tasks depends on the maximum value we have for each abilities.

For example, if we only had one $a >= N$ and another $b >= M$, the probability $p$ is 1/12. If we had k refresh chances, the probability increased to $p_k$=1-(11/12)^3 = `r 1-(11/12)^3`. If we had one $a >= N$, and $b_1$, $b_2$ $>= M$, then $p$ = 2/12.

To calculate the probability, first find the count A of $a_i >= N$. Then find the count B of $b_i >= M$.

If A<2,     p=0;

If A>=B>=2, p=(2!choose(B,2)+(A-B)*B))/12;

If A>=B>=1, A>=2,B<2, p=(A-B)*B))/12;

Note1: choose(0,2) and choose(1,2) are both 0
Note2: If A < 2, B most < 2

So we can use P=(2!choose(B,2)+(A-B)*B))/12 for all conditions


### Question 2：Given another length 4 vector E, only one component of E can be used to be added to the corresponding position of V to fulfill task 1. What is the probability now (task 2).

Given E, the final number of a>=N and b>=M combinations is the union of each new combinations after adding one $e_i$ to the corresponding component $v_i$ in V.

We can separate the final possibility calculation into following steps:

Step 1: Obtain the numbers of combinations of the set $VE_i = V + e_i$, i=1:4.

Step 2: Calculate the probability $p_0$ for the union of combinations in Step 1.  

Step 3: Calculate the final $p_1$ as 1-(1-$p_0$)^(1+refresh times)

For step 1 and 2:

Since we only add one $e_i$ a time, it affects one component $v_i$ only. Thus any new combinations after adding $e_i$ will be different from the new combinations after adding another $e_i$. We only need to add the number of new combinations $\Delta C_{ve_i}$  with the number of combinations $C_v$ for the original vector V.  


<br>


* Function 1: Given reflash times f, your maxmum two sums of each ability as vector V, your elf maxmum bonus for each ability E, what is the probability to complete task in level X of requirement R

```{r}
P1<-function(f=2,R=c(20,18),
             V=c("F"=18,"D"=18,"K"=18,"S"=18),
             E=c("F"=6,"D"=0,"K"=6,"S"=4)
){
  N<-min(R)
  M<-max(R)
  A1<-sum(V>=N)
  B1<-sum(V>=M)
  P0=(choose(B1,2)*factorial(2)+(A1-B1)*B1)/12
  P=P0
  print(paste("Given V, ",A1," and ",B1," fulfill requirement ", N,", ",M, ", P0 = ",round(P,3),sep=""))
  if(A1>=1){# if none of them are at least N, it is impossible to fullfill the requirement
    for(a in names(V)){
      VE=V[a]+E[a]
      Vnew=V
      Vnew[a]<-VE
      A2<-sum(Vnew>=N)
      B2<-sum(Vnew>=M)
      P1=(choose(B2,2)*factorial(2)+(A2-B2)*B2)/12
      deltaP=P1-P0
      P=P+deltaP
      print(paste("Adding E to position ", a,", ",A2," and ",B2," fulfill requirement, ", round(deltaP,3)," more likely now",sep=""))
    }
    P2<-1-(1-P)^(f+1)
    print(paste("With refresh times ",f,", P0 increased from ",round(P,3)," to ",round(P2,3),sep=""))
  }
  else(print("No possible combinations to fulfill the requirement"))
}
##test
P1()
P1(f=0,V=c("F"=18,"D"=18,"K"=16,"S"=16),E=c("F"=0,"D"=0,"K"=0,"S"=0))
P1(f=0,V=c("F"=18,"D"=18,"K"=16,"S"=16),E=c("F"=6,"D"=0,"K"=0,"S"=0))
P1(f=0,V=c("F"=18,"D"=18,"K"=16,"S"=16),E=c("F"=6,"D"=0,"K"=6,"S"=0))
```
<br>

### Question 3: Given a list of 4 vectors V0, get the max sum for each vector as the vector V for Question 1. Each sum can used up to 2 components.

### Question 4: Given V0 and E, get the max sum of each vector as sum of the V0 vector and the corresponding E component, can only use up to 1 component in E and up to total of 4 component in V0.

### Question 5: Given V0 and E, what is the minimum value to be add to which component in V0 or E to fulfill a certain probability in task 2.


## Backgroud

Daily task list could have several S+ tasks, maximum hometown level requires 20 and 18 points of randomly selected two out of four abilities to complete S+ task. Original S rank Valkyries contribute 8, 10, 12 points in rank S, SS and SSS. Original A rank Valkyries contribute points in rank A to SSS, and original B rank Valkyries contribute points from rank B to SSS. Free elves Jingwei's Wing contributes 1-4 Dexterity points for rank A to SSS and Blood embrace gives 1-4 points in Fitness.

```{r,echo=FALSE,results='asis'}
library(knitr)
# dexterity
# yae, mei, ice elf
# fitness
# kiana, fuhua, blood elf
# knowledge
# terisa, bronya
# speech
# Himeko, kallen, jingwei elf

contribute_Srank<-data.frame("rank"=c("S","SS","SSS"),"value"=c(8,10,12))
contribute_Arank<-data.frame("rank"=c("A","S","SS","SSS"),"value"=c(2,3,4,6))
contribute_Brank<-data.frame("rank"=c("B","A","S","SS","SSS"),"value"=c(1,1,2,3,4))


#kable(contribute_Srank,caption="S rank Valkyries")
#kable(contribute_Srank,caption="A rank Valkyries")
#kable(contribute_Srank,caption="B rank Valkyries")

```

<br>

Same Valkyries usually have same ability except several newly added ones.Free and paid elves also had abilities.

```{r,echo=FALSE}
#Jingwei's Wing: 1-4 d
#Blood embrace:  1-4 f
#Klein: 6 k
#Blade Durandal: 6 f
#Selune's Elegy:d
#Book of fuxi:k
#water's edge:d
#Tesla zero:s
#Beela :f
#Sirin:k
contribute_Felf<-data.frame("star"=c("2","3","4"),"value"=c(2,3,4))
contribute_Pelf<-data.frame("star"=c("2","3","4"),"value"=c(6,7,8))
#kable(contribute_Srank,caption="Free elves")
#kable(contribute_Srank,caption="Paid elves")
```

